Verifying Demonstrations

### 2018-02-26 paper/SystemModel.tex
manet references, MANETs.tex, issue 28, included in system model

In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
Section~\ref{protocol} and uploading their testimony to a blockchain
after the protest.

More formally, we use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

@@

>>>>

We use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

@@

\subsection{Physical System Model}
In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
Section~\ref{protocol} and uploading their testimony to a blockchain
after the protest. They thus need connectivity at least to each other
during the protest and Internet connectivity after.

\include*{MANETs}
